---
title: "Pilot analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format:
  html:
    toc: true
    toc-location: left
    toc-expand: true
    df-print: paged
---

# Set up

```{r setup}
#| echo: false
#| results: hide
#| warning: false

library(tidyverse); theme_set(theme_bw())
library(readr)
library(flextable)
library(lme4)

#practice <- read_csv("~/Documents/Research/Coreference/Name #Survey/Pilot/2023-12-11/data_exp_150132-v4/data_exp_150132-v4_task-smjw.csv")
#demog <- read_csv("~/Documents/Research/Coreference/Name #Survey/Pilot/2023-12-11/data_exp_150132-v4/data_exp_150132-v4_questionnaire-i6tq.csv")
#raw_data <- read_csv("~/Documents/Research/Coreference/Name #Survey/Pilot/2023-12-11/data_exp_150132-v4/data_exp_150132-v4_task-9t9c.csv")

names_combined <- read_csv("data/large_files/names_combined.csv", show_col_types = FALSE)

practiceV3 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v3/data_exp_150132-v3_task-smjw.csv",
                       show_col_types = FALSE)
demogV3 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v3/data_exp_150132-v3_questionnaire-i6tq.csv",
                       show_col_types = FALSE)
raw_dataV3 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v3/data_exp_150132-v3_task-9t9c.csv",
                       show_col_types = FALSE)

practiceV4 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v4/data_exp_150132-v4_task-smjw.csv",
                       show_col_types = FALSE)
demogV4 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v4/data_exp_150132-v4_questionnaire-i6tq.csv",
                       show_col_types = FALSE)
raw_dataV4 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v4/data_exp_150132-v4_task-9t9c.csv",
                       show_col_types = FALSE)

practiceV5 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v5/data_exp_150132-v5_task-smjw.csv",
                       show_col_types = FALSE)
demogV5 <-    read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v5/data_exp_150132-v5_questionnaire-i6tq.csv",
                       show_col_types = FALSE)
raw_dataV5 <- read_csv("~/Documents/Research/Coreference/Name Survey/Pilot/2023-12-19/data_exp_150132-v5/data_exp_150132-v5_task-9t9c.csv",
                       show_col_types = FALSE)
```

```{r}
practice_data_all <- practiceV3 |> mutate(version = 3) |> 
  rbind(practiceV4 |> mutate(version = 4)) |> 
  rbind(practiceV5 |> mutate(version = 5))

demographics_all <- demogV3 |> mutate(version = 3) |> 
  rbind(demogV4 |> mutate(version = 4)) |> 
  rbind(demogV5 |> mutate(version = 5))

raw_data_all <- raw_dataV3 |> mutate(version = 3) |> 
  rbind(raw_dataV4 |> mutate(version = 4)) |> 
  rbind(raw_dataV5 |> mutate(version = 5))
```

Clean up.

```{r}
rm(practiceV3, practiceV4, practiceV5,
   demogV3, demogV4, demogV5,
   raw_dataV3, raw_dataV4, raw_dataV5)
```


Combine practice, rating and demographic data

```{r}
practice_data_all |> 
  filter(!is.na(Display),
         `Response Type` == "response") |> 
  select(`Participant Private ID`, `Participant Status`, 
         version, #`Task Version`, 
         `Spreadsheet: display`, `Spreadsheet: name`,
         `Object Name`, Response) |> 
  mutate(freq_block = NA) |> 
  pivot_wider(names_from = "Object Name",
              values_from = "Response") |> 
  rename(participant = `Participant Private ID`,
         status = `Participant Status`,
         #practice.version = `Task Version`,
         task = `Spreadsheet: display`,
         name = `Spreadsheet: name`,
         masc = `Masc Slider`,
         fem = `Fem Slider`,
         neut = `Neut slider`,
         comment = `Text Entry`) |> 
  mutate(#participant = as.numeric(as.factor(participant)),
         freq_block = as.factor(freq_block),
         masc = as.numeric(masc),
         fem = as.numeric(fem),
         neut = as.numeric(neut)) -> practice_clean
```

```{r}
demographics_all |> 
  filter(Key == "value") |> 
  select(`Participant Private ID`, `Participant Status`, 
         version, #`Task Version`, 
         #Question,
         `Object Name`, Response) |> 
  pivot_wider(names_from = `Object Name`,
              values_from = Response) |> 
  rename(participant = `Participant Private ID`,
         status = `Participant Status`,
         #practice.version = `Task Version`,
         #question = Question,
         gender.free = `Gender free text`,
         gender.cat = `Gender Dropdown`,
         asb = `ASB Dropdown`,
         familiarity = `Familiarity Dropdown`,
         location.childhood = Childhood,
         location.adulthood = Adulthood,
         ethnicity = `Ethnicity-comment`,
         location.longest = `Lived longest`,
         location.influence = `Biggest influence`,
         birthyear = `Your age`,
         parent1 = `Parent 1`,
         parent2 = `Parent 2`,
         gpar1 = `Grandparent 1`,
         gpar2 = `Grandparent 2`,
         gpar3 = `Grandparent 3`,
         gpar4 = `Grandparent 4`,
         child1 = `Oldest Child`,
         child2 = `Youngest Child`,
         gchild1 = `Oldest Grandchild`,
         gchild2 = `Youngest Grandchild`,
         exp.comment = `Comment Box`) |> 
  mutate(birthyear = as.numeric(birthyear),
         parent1   = as.numeric(parent1),
         parent2   = as.numeric(parent2),
         gpar1     = as.numeric(gpar1  ),
         gpar2     = as.numeric(gpar2  ),
         gpar3     = as.numeric(gpar3  ),
         gpar4     = as.numeric(gpar4  ),
         child1    = as.numeric(child1 ),
         child2    = as.numeric(child2 ),
         gchild1   = as.numeric(gchild1),
         gchild2   = as.numeric(gchild2)) -> demog_clean
```

```{r}
raw_data_all |> 
  filter(!is.na(Response),!is.na(Display)) |> 
  select(`Participant Private ID`, `Participant Status`, 
         version, #`Task Version`, 
         `Spreadsheet: display`, `Spreadsheet: name`, `Spreadsheet: freq_block`,
         `Object Name`,`Response`) |> 
  pivot_wider(names_from = "Object Name",
              values_from = "Response") |> 
  rename(participant = `Participant Private ID`,
         status = `Participant Status`,
         task = `Spreadsheet: display`,
         name = `Spreadsheet: name`,
         freq_block = `Spreadsheet: freq_block`,
         masc = `Masc Slider`,
         fem = `Fem Slider`,
         neut = `Neut slider`,
         comment = `Text Entry`) |> 
  mutate(#participant = as.numeric(as.factor(participant)),
         freq_block = as.factor(freq_block),
         masc = as.numeric(masc),
         fem = as.numeric(fem),
         neut = as.numeric(neut)) -> ratings_clean
```

all in one file:

```{r}
practice_clean |> 
  rbind(ratings_clean) |> 
  left_join(demog_clean, 
            by = join_by(participant, status, version)) -> rating_data
```


How many ratings for each name?

```{r}
rating_data |> 
  group_by(name, freq_block) |> summarise(n = n(), .groups = "drop") |> 
  arrange(desc(n))
```


# Govt Name Corpus info

Create a breakdown of the absolute value of the log of the ratio of ASABs for the population data across all years and regions. (This can be distinguished in more detail in other ways.)

```{r}
names_combined |> 
    # not useful right now
  select(-c(rank, proportion)) |> 
    # remove default baby names
  filter(!name %in% c("Baby","Infant","Female","Notnamed","Stillborn","Unborn","Unnamed","Unknown","Unkown")) |> 
  pivot_wider(names_from = asab,
              values_from = number,
              values_fill = NA) |> 
  rename(afab = `F`, amab = M) |> 
  group_by(name) |> 
  summarise(log.ratio = (sum(afab, na.rm = TRUE)/sum(amab, na.rm = TRUE)) |> log() |> abs(),
            regions = n_distinct(region),
            years = n_distinct(year),
            total_afab = sum(afab, na.rm = TRUE),
            total_amab = sum(amab, na.rm = TRUE),
            total_people = sum(afab, na.rm = TRUE)+sum(amab, na.rm = TRUE),
            .groups = "drop") |> #view() #
  mutate(log.ratio = case_when(log.ratio > 1000 ~ NA,
                               .default = log.ratio)) -> combined.breakdown; combined.breakdown
```


In the combined name corpus, there are `r names_combined |> pull(name) |> length() |> format(big.mark = ",")` entries, with `r names_combined |> filter(asab == "F") |> pull(name) |> length() |> format(big.mark = ",")` of them registered for babies assigned female at birth (AFAB) and `r names_combined |> filter(asab == "M") |> pull(name) |> length() |> format(big.mark = ",")` registered for babies assigned male at birth (AMAB). This means that `r ((names_combined |> filter(asab == "F") |> pull(name) |> length()) / (names_combined |> pull(name) |> length())) |> scales::percent(accuracy = 0.01)` of the entries in this database are for names registered to AFAB babies. This results in `r names_combined |> pull(name) |> unique() |> length() |> format(big.mark = ",")` unique names spread over `r names_combined |> pull(region) |> unique() |> length()` regions across all years (which are detailed below).

```{r}
#| echo: false
# number of years per region
names_combined |> group_by(region) |> 
  summarise(`Earliest year` = min(year),
            `Latest year` = max(year),
            `Total range of years` = max(year)-min(year) + 1, # inclusive years
            .groups = "drop") |> 
  arrange(-`Total range of years`) |> 
  flextable() |> 
  width(width = 6) |> 
  colformat_double(big.mark = "", digits = 0)
```


How many unisex names? (unique)
How many of the names in the database are attested for both AFAB and AMAB babies?
How many of the names in the rating set are attested for both AFAB and AMAB babies?

```{r}
#| echo: false
names_combined |> 
  group_by(name,asab) |> 
  summarise(n = n(), .groups = "drop") |> 
  pivot_wider(names_from = asab,
              values_from = n) |> 
  rename(fem = `F`, msc = `M`) -> name_counts
```

In the database, there are `r name_counts |> filter(!is.na(fem),!is.na(msc)) |> pull(name) |> length() |> format(big.mark = ",")` names that are attested at least once for both AMAB and AFAB babies across all years. Of these names, `r name_counts |> filter(!is.na(fem),!is.na(msc), name %in% unique(rating_data$name)) |> pull(name) |> length() |> format(big.mark = ",")` have been rated for gender typicality at least once.

In the database, there are `r name_counts |> filter(!is.na(fem),is.na(msc)) |> pull(name) |> length() |> format(big.mark = ",")` names that are attested at least once for AFAB babies across all years, but never for AMAB babies. Of these names, `r name_counts |> filter(!is.na(fem),is.na(msc), name %in% unique(rating_data$name)) |> pull(name) |> length() |> format(big.mark = ",")` have been rated for gender typicality at least once.

In the database, there are `r name_counts |> filter(is.na(fem),!is.na(msc)) |> pull(name) |> length() |> format(big.mark = ",")` names that are attested at least once for AMAB babies across all years, but never for AFAB babies. Of these names, `r name_counts |> filter(is.na(fem),!is.na(msc), name %in% unique(rating_data$name)) |> pull(name) |> length() |> format(big.mark = ",")` have been rated for gender typicality at least once.

A separate question is whether a name is considered unisex overall or whether it should be determined on a yearly and/or regional basis.

## breakdowns

```{r}
names_combined |> 
    # not useful right now
  select(-c(rank, proportion)) |> 
    # remove default baby names
  filter(!name %in% c("Baby","Infant","Female","Notnamed","Stillborn","Unborn","Unnamed","Unknown","Unkown")) |> 
  pivot_wider(names_from = asab,
              values_from = number,
              values_fill = 0) |> 
  rename(afab = `F`, amab = M) |> 
  mutate(annual.regional.log.ratio = case_when(afab > 0 & amab > 0 ~ abs(log(afab/amab)),
                                               .default = NA)) -> annual.regional.breakdown

names_combined |> 
    # not useful right now
  select(-c(rank, proportion)) |> 
    # remove default baby names
  filter(!name %in% c("Baby","Infant","Female","Notnamed","Stillborn","Unborn","Unnamed","Unknown","Unkown")) |> 
  pivot_wider(names_from = asab,
              values_from = number,
              values_fill = NA) |> 
  rename(afab = `F`, amab = M) |> 
  group_by(name,year) |> 
  summarise(annual.log.ratio = (sum(afab, na.rm = TRUE)/sum(amab, na.rm = TRUE)) |> log() |> abs(),
            regions = n_distinct(region),
            total_afab = sum(afab, na.rm = TRUE),
            total_amab = sum(amab, na.rm = TRUE),
            total_people = sum(afab, na.rm = TRUE)+sum(amab, na.rm = TRUE),
            .groups = "drop") |> #view() #
  mutate(annual.log.ratio = case_when(annual.log.ratio > 1000 ~ NA,
                                      .default = annual.log.ratio)) -> annual.breakdown

names_combined |> 
    # not useful right now
  select(-c(rank, proportion)) |> 
    # remove default baby names
  filter(!name %in% c("Baby","Infant","Female","Notnamed","Stillborn","Unborn","Unnamed","Unknown","Unkown")) |> 
  pivot_wider(names_from = asab,
              values_from = number,
              values_fill = NA) |> 
  rename(afab = `F`, amab = M) |> 
  group_by(name,region) |> 
  summarise(regional.log.ratio = (sum(afab, na.rm = TRUE)/sum(amab, na.rm = TRUE)) |> log() |> abs(),
            years = n_distinct(year),
            total_afab = sum(afab, na.rm = TRUE),
            total_amab = sum(amab, na.rm = TRUE),
            total_people = sum(afab, na.rm = TRUE)+sum(amab, na.rm = TRUE),
            .groups = "drop") |> #view() #
  mutate(regional.log.ratio = case_when(regional.log.ratio > 1000 ~ NA,
                                        .default = regional.log.ratio)) -> regional.breakdown

names_combined |> 
    # not useful right now
  select(-c(rank, proportion)) |> 
    # remove default baby names
  filter(!name %in% c("Baby","Infant","Female","Notnamed","Stillborn","Unborn","Unnamed","Unknown","Unkown")) |> 
  pivot_wider(names_from = asab,
              values_from = number,
              values_fill = NA) |> 
  rename(afab = `F`, amab = M) |> 
  group_by(name) |> 
  summarise(log.ratio = (sum(afab, na.rm = TRUE)/sum(amab, na.rm = TRUE)) |> log() |> abs(),
            regions = n_distinct(region),
            years = n_distinct(year),
            total_afab = sum(afab, na.rm = TRUE),
            total_amab = sum(amab, na.rm = TRUE),
            total_people = sum(afab, na.rm = TRUE)+sum(amab, na.rm = TRUE),
            .groups = "drop") |> #view() #
  mutate(log.ratio = case_when(log.ratio > 1000 ~ NA,
                               .default = log.ratio)) -> combined.breakdown
```


# Raw data

How many ratings for each name in the three different categories, as defined above?

```{r}
rating_data |> 
  filter(name %in% (name_counts |> filter(!is.na(fem),!is.na(msc)) |> pull(name))) |> 
  group_by(name, freq_block) |> summarise(n = n(), .groups = "drop") |> 
  arrange(-n)

rating_data |> 
  filter(name %in% (name_counts |> filter(!is.na(fem),is.na(msc)) |> pull(name))) |> 
  group_by(name, freq_block) |> summarise(n = n(), .groups = "drop") |> 
  arrange(-n)

rating_data |> 
  filter(name %in% (name_counts |> filter(is.na(fem),!is.na(msc)) |> pull(name))) |> 
  group_by(name, freq_block) |> summarise(n = n(), .groups = "drop") |> 
  arrange(-n)
```

> TO DO: in next iteration, include frequency data and/or log.ratio in this analysis


```{r}
#| warning: false
##| fig-width: 12
##| fig-height: 6.5

filter_name <-  #c("Charlie")
                c("Alex","Andrea","Ashley","Charlie","Jamie",
                  "Lee","Morgan","Robin","Riley","Dale","Sam",
                  "James","William","Edward",# original stopped here
                  #"Godzilla",
                  "Mary","Shannon","Julia","John","Elizabeth",
                  "Laura","Charley","Jordan",
                  "Cameron","Gabriel","Jean","Jessie","Nicola","Terry"); rating_data |> 
  filter(name %in% filter_name) |> 
  ggplot(aes(x = fem, 
             y = masc)) +
  geom_density2d_filled(contour_var = "ndensity") +
  geom_point(#aes(color = neut),
             color = "black",
             shape = 4,
             alpha = .5) +
  
#  # NOT GOOD YET BECAUSE WHITE DOT CANT BE IN TOP RIGHT CORNER ... YET
#  geom_point(#inherit.aes = FALSE,
#             data = combined.breakdown |> 
#               filter(name %in% filter_name) |> 
#               mutate(max.asab = case_when(total_afab > total_amab ~ total_afab,
#                                           .default = total_amab),
#                      fem  = (total_afab/total_people)*100,
#                      masc = (total_amab/total_people)*100),
#             shape = 21, fill = "gray80", color = "white", size = 1, alpha = .9) +
#  # USE PROPORTION OF LARGER OF TWO ASAB COUNTS
#  geom_point(data = combined.breakdown |> 
#               filter(name %in% filter_name) |> 
#               mutate(max.asab = case_when(total_afab > total_amab ~ total_afab,
#                                           .default = total_amab),
#                      fem  = (total_afab/max.asab)*100,
#                      masc = (total_amab/max.asab)*100),
#             shape = 21, fill = "gray80", color = "white", size = 1, alpha = .9) +
#  # COMBINE THE TWO STRATEGIES
#  geom_point(data = combined.breakdown |> 
#               filter(name %in% filter_name) |> 
#               mutate(max.asab = case_when(total_afab > total_amab ~ total_afab,
#                                           .default = total_amab),
#                      fem  = (((total_afab/max.asab)+(total_afab/total_people))/2)*100,
#                      masc = (((total_amab/max.asab)+(total_amab/total_people))/2)*100),
#             shape = 21, fill = "white", color = "gray80", size = 3, alpha = .9) +
#  
#  # REGIONAL POINTS 
#  geom_point(data = regional.breakdown |> 
#               filter(name %in% filter_name) |> 
#               mutate(max.asab = case_when(total_afab>total_amab~total_afab,
#                                           .default = total_amab),
#                      max.f.prop = total_afab/max.asab,
#                      total.f.prop = total_afab/total_people,
#                      max.m.prop = total_amab/max.asab,
#                      total.m.prop = total_amab/total_people,
#                      fem  = ((max.f.prop+total.f.prop)/2)*100,
#                      masc = ((max.m.prop+total.m.prop)/2)*100),
#             shape = 23, fill = "violet", color = "white", size = 2, alpha = 1, nudge_x = 5) +
#  ggrepel::geom_text_repel(data = regional.breakdown |> 
#                             filter(name %in% filter_name) |> 
#                             mutate(max.asab = case_when(total_afab>total_amab~total_afab,
#                                                         .default = total_amab),
#                                    max.f.prop = total_afab/max.asab,
#                                    total.f.prop = total_afab/total_people,
#                                    max.m.prop = total_amab/max.asab,
#                                    total.m.prop = total_amab/total_people,
#                                    fem  = ((max.f.prop+total.f.prop)/2)*100,
#                                    masc = ((max.m.prop+total.m.prop)/2)*100),
#                           aes(label = region),
#                           shape = 4, fill = "white", color = "black", size = 2, alpha = 1, #nudge_x = 5,
#                           max.overlaps = 10) +
  
  scale_fill_viridis_d(option = "turbo", begin = .1) +
  scale_x_continuous(limits = c(0,100),labels = scales::percent_format(scale = 1)) +
  scale_y_continuous(limits = c(0,100),labels = scales::percent_format(scale = 1)) +
  facet_wrap(~name, ncol = 7) + 
  theme(legend.position = "none") +
  coord_equal() +
  NULL
```

## combined visuals

```{r}
#| warning: false
filter_name <- c("Morgan"); annual.regional.breakdown |> 
  filter(name %in% filter_name) |>  # NEED TO DEFINE FILTERED NAMES atio) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max)) |> 
  ungroup() |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> filter(name %in% filter_name),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  geom_point(data = rating_data |> filter(name %in% filter_name),
                        aes(x = fem/100,
                            y = masc/100),
             color = "black",
             shape = 4,
             alpha = .5) +
  
  
  geom_point(aes(color = region), 
             color = "red",
             alpha = .75, 
             size = 2, 
             shape = 16) +
  geom_density2d(color = "red", bins = 75) +
  geom_path(aes(group = region, color = region),
            color = "red4",
            size = 0.5,
            alpha = 0.5) +
  #ggrepel::geom_text_repel(aes(label = year),
  #                         size = 2,
  #                         color = "red",
  #                         max.overlaps = 20) +
  
  
  geom_abline(slope = 1, intercept = 0) +
  facet_wrap(~ name) +
  #scale_color_viridis_d(option = "turbo", begin = .9, end = .1) +
  #scale_fill_viridis_b(option = "")
  scale_fill_grey() +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  facet_wrap(~region) +
  theme(legend.position = "none")
```


```{r}
#| warning: false
filter_name <- c("James","Gabriel","Morgan",
                 "Charlie","Riley","Nicola",
                 "Leslie","Ashley","Elizabeth"); annual.regional.breakdown |> 
  filter(name %in% filter_name) |>  # NEED TO DEFINE FILTERED NAMES ratio) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max)) |> 
  ungroup() |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> filter(name %in% filter_name),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  #geom_point(data = rating_data |> filter(name %in% filter_name),
  #                      aes(x = fem/100,
  #                          y = masc/100),
  #           color = "black",
  #           shape = 4,
  #           alpha = .5) +
  
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  #geom_point(aes(color = region), 
  #           color = "red",
  #           alpha = .75, 
  #           size = 2, 
  #           shape = 16) +
  #geom_density2d(color = "red", bins = 75) +
  geom_density2d_filled(contour_var = "ndensity", aes(alpha = after_stat(level))) +
  #geom_path(aes(group = region, color = region),
  #          color = "red4",
  #          size = 0.5,
  #          alpha = 0.5) +
  #ggrepel::geom_text_repel(aes(label = year),
  #                         size = 2,
  #                         color = "red",
  #                         max.overlaps = 20) +
  
  
  #geom_abline(slope = 1, intercept = 0) +
  #scale_fill_viridis_d(option = "mako", begin = .1, end = .9) +
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none") +
  #facet_wrap(~region) +
  facet_wrap(~ factor(name, levels = c("James","Gabriel","Leslie",
                                       "Charlie","Riley","Nicola",
                                       "Morgan","Ashley","Elizabeth"))) +
  NULL
```

### check out all most-rated names

```{r}
#| warning: false

filter_name <- rating_data |> 
  group_by(name, freq_block) |> summarise(n = n(), .groups = "drop") |> 
  filter(n > 10) |> pull(name); annual.regional.breakdown |> 

  filter(name %in% filter_name) |>
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max)) |> 
  ungroup() |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> filter(name %in% filter_name),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  geom_density2d_filled(contour_var = "ndensity", aes(alpha = after_stat(level))) +

  geom_abline(slope = 1, intercept = 0, color = "white") +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none") +
  facet_wrap(~name) +
  NULL
```



```{r}
filter_name <- c("Alex","Andrea","Ashley","Charlie","Jamie",
                  "Lee","Morgan","Robin","Riley","Dale","Sam",
                  "James","William","Edward",# original stopped here
                  #"Godzilla",
                  "Mary","Shannon","Julia","John","Elizabeth",
                  "Laura","Charley","Jordan",
                  "Cameron","Gabriel","Jean","Jessie","Nicola","Terry"); 
filter_name <- c("Charlie","Charley"); annual.regional.breakdown |> 
  filter(name %in% filter_name) |>  # NEED TO DEFINE FILTERED NAMES atio) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         angle = atan2(y = amab/yr.max, x = afab/yr.max),
         hemi = angle/pi,
         degrees = hemi*180,
         plot.degrees = round(degrees, digits = 0)-45) |> 
  ungroup() |> 
  #filter(degrees>0 & degrees<90) |> 
  ggplot(aes(x = plot.degrees, fill = plot.degrees, group = plot.degrees)) +
  #geom_histogram(binwidth = 1) +
  geom_bar()+
  scale_x_continuous(breaks = seq(from = -45, to = 45, by = 5)) +
  scale_fill_gradient2(low = "green3", high = "orangered", mid = "gold", na.value = "black") +
  scale_y_log10() +
  #facet_wrap(~name) +
  facet_grid(region~name, scales = "free_y") +
  NULL
```

(could I turn this into a gauge needle visualization?)

### other demog dimensions?

```{r}
#| warning: false
filter_name <- "Morgan"; annual.regional.breakdown |> 

  filter(name %in% filter_name) |>
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |> 
  ungroup() |> 
  filter(decade >= 1940) |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name) |> 
                          mutate(decade = round(birthyear, digits = -1)) |> 
                          filter(decade >= 1940),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  geom_density2d_filled(contour_var = "ndensity", aes(alpha = after_stat(level))) +

  geom_abline(slope = 1, intercept = 0, color = "white") +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none") +
  facet_grid(decade~region) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  NULL
```

### by decade

```{r}
rating_data |> 
  filter(name == "Morgan") |>
  mutate(location.influence = case_when(location.influence == "__other" ~ location.longest,
                                        .default = location.influence),
         location = case_when(location.influence %in% c("Canada",
                                                        "United States of America") ~ "North America",
                              location.influence %in% c("UK - England and Wales",
                                                        "Ireland",
                                                        "UK - Scotland",
                                                        "Australia",
                                                        "New Zealand") ~ "Islands")) |> 
  #group_by(location) |> summarise(n = n())
  ggplot(aes(x = birthyear, fill = location)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~location)
```

```{r}
annual.regional.breakdown |> 
  filter(name == "Morgan",
         year >= 1945,
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North America",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland",
                                          "Australia",
                                          "New Zealand") ~ "Islands")) |> 
  #group_by(region) |> summarise(n = n())
  ggplot(aes(x = year, fill = region)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~region)
```

```{r}
#| warning: false
filter_name <- "Morgan"; annual.regional.breakdown |> 
  filter(name %in% filter_name,
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North America",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |> 
  ungroup() |> 
  filter(decade >= 1950) |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name) |>
                          mutate(decade = round(birthyear+15, digits = -1),
                                 location.influence = case_when(location.influence == "__other" ~ location.longest,
                                                                .default = location.influence),
                                 region = case_when(location.influence %in% c("Canada","United States of America") ~ "North America",
                                                    location.influence %in% c("UK - England and Wales","Ireland","UK - Scotland") ~ "Europe",
                                                    location.influence %in% c("Australia","New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1950),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  geom_density2d_filled(contour_var = "ndensity", aes(alpha = after_stat(level))) +

  geom_abline(slope = 1, intercept = 0, color = "white", linewidth = .5, alpha = .5) +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none") +
  facet_grid(region~decade) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  xlab("afab/typicality") +
  ylab("amab/typicality") +
  ggtitle(paste0("Population influence on ratings for the name ",filter_name," over decades and regions"),
          subtitle = "Grayscale = population; Color = ratings; Age of influence = birthyear + 15") +
  NULL
```

```{r}
#| warning: false
rating_data |>
  mutate(decade = round(birthyear, digits = -1),
         location.influence = case_when(location.influence == "__other" ~ location.longest,
                                        .default = location.influence),
         region = case_when(location.influence %in% c("Canada",
                                                      "United States of America") ~ "North America",
                            location.influence %in% c("UK - England and Wales",
                                                      "Northern Ireland",
                                                      "Ireland",
                                                      "UK - Scotland") ~ "Europe",
                            location.influence %in% c("Australia",
                                                      "New Zealand") ~ "Oceania")) |> 
  group_by(name, region) |> summarise(n = n(), .groups = "drop") |> 
  arrange(-n) |> 
  pivot_wider(names_from = region,
              values_from = n) |> 
  arrange(desc(Oceania)) |> filter(Oceania >= 3) |> pull(name) -> filter_name; annual.regional.breakdown |> 
  filter(name %in% filter_name,
         name != "Godzilla",
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North\nAmerica",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |> 
  ungroup() |> 
  filter(decade >= 1950) |> 
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(location.influence == "__other" ~ location.longest,
                                                                .default = location.influence),
                                 region = case_when(location.influence %in% c("Canada","United States of America") ~ "North\nAmerica",
                                                    location.influence %in% c("UK - England and Wales","Ireland","UK - Scotland") ~ "Europe",
                                                    location.influence %in% c("Australia","New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1950),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  geom_point(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(location.influence == "__other" ~ location.longest,
                                                                .default = location.influence),
                                 region = case_when(location.influence %in% c("Canada","United States of America") ~ "North\nAmerica",
                                                    location.influence %in% c("UK - England and Wales","Ireland","UK - Scotland") ~ "Europe",
                                                    location.influence %in% c("Australia","New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1950),
                        aes(x = fem/100,
                            y = masc/100),
             color = "black",
             shape = 4,
             size = 1,
             alpha = .5) +
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  geom_density2d_filled(contour_var = "ndensity", aes(alpha = after_stat(level))) +

  geom_abline(slope = 1, intercept = 0, color = "white", linewidth = .5, alpha = .5) +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(decade~name*region) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  xlab("afab/typicality") +
  ylab("amab/typicality") +
  ggtitle(paste0("Population influence on ratings for the name ",filter_name," over decades and regions"),
          subtitle = "Grayscale = population; Color = ratings; Age of influence = birthyear") +
  NULL
```

```{r}
rating_data |>
  mutate(decade = round(birthyear, digits = -1),
         location.influence = case_when(location.influence == "__other" ~ location.longest,
                                        .default = location.influence),
         region = case_when(location.influence %in% c("Canada",
                                                      "United States of America") ~ "North America",
                            location.influence %in% c("UK - England and Wales",
                                                      "Northern Ireland",
                                                      "Ireland",
                                                      "UK - Scotland") ~ "Europe",
                            location.influence %in% c("Australia",
                                                      "New Zealand") ~ "Oceania")) |> 
  group_by(name, region) |> summarise(n = n(), .groups = "drop") |> 
  arrange(-n) |> 
  pivot_wider(names_from = region,
              values_from = n) |> 
  arrange(desc(Europe)) |> 
  filter(Europe >= 5, Oceania >=3 ) |> pull(name) -> top_rate_eu
```

#### by decade for population only

```{r}
#| warning: false
names_combined |> 
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North\nAmerica",
                            region %in% c("England and Wales",
                                          "Northern Ireland",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name, region) |> 
  summarise(sum = sum(number),
            .groups = "drop") |> 
  group_by(region) |> 
  mutate(rank = rank(-sum, ties.method = "first")) |> 
  arrange(rank) |> 
  filter(rank <= 100) |> pull(name) -> top_pop
```


```{r}
#| warning: false
#intersect(top_pop, top_rate_eu)
set.seed(231);top_rate_eu -> filter_name; annual.regional.breakdown |> 
  filter(name %in% filter_name,
         name != "Godzilla",
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North\nAmerica",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         #log10.afab = case_when(afab > 0 ~ log10(afab), .default = abs(rnorm(1,sd=0.001))),
         #log10.amab = case_when(amab > 0 ~ log10(amab), .default = abs(rnorm(1,sd=0.001))),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |>
  ungroup() |> 
  filter(decade >= 1960) |> #filter(name == "Andrea") |> #summary()
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(location.influence == "__other" ~ location.longest,
                                                                .default = location.influence),
                                 region = case_when(location.influence %in% c("Canada","United States of America") ~ "North\nAmerica",
                                                    location.influence %in% c("UK - England and Wales","Ireland","UK - Scotland") ~ "Europe",
                                                    location.influence %in% c("Australia","New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1960),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity") +
  geom_point(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(location.influence == "__other" ~ location.longest,
                                                                .default = location.influence),
                                 region = case_when(location.influence %in% c("Canada","United States of America") ~ "North\nAmerica",
                                                    location.influence %in% c("UK - England and Wales","Ireland","UK - Scotland") ~ "Europe",
                                                    location.influence %in% c("Australia","New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1960),
                        aes(x = fem/100,
                            y = masc/100),
             color = "black",
             shape = 4,
             size = 1,
             alpha = .5) +
  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  #geom_density2d() +
  #geom_point(alpha = .5, shape = 3, color = "violet") +
  geom_density2d_filled(aes(alpha = after_stat(level)),
                        contour_var = "ndensity", bins = 50) +

  geom_abline(slope = 1, intercept = 0, color = "white", linewidth = .5, alpha = .5) +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.5,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(name*region~decade) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  xlab("afab/typicality") +
  ylab("amab/typicality") +
  ggtitle(paste0("Population influence on ratings for the name ",filter_name," over decades and regions"),
          subtitle = "Grayscale = population; Color = ratings; Age of influence = birthyear") +
  NULL
```

- Select a name or set of names. 
- Then, take the annual regional summary and filter to create a subset of population data.
- Group the regions into three groups (North America, Europe, and Oceania), since these three groups have broadly similar influences and could therefore have similar trends and cultural exchanges.
- Next, for each name in each region, calculate the total number of years of data.
- Take the log-base-10 of the number of attestations for each name for each ASAB.
- Divide the log attestations by the number of years to calculate the average number of log-attestation per log-year (this is weird, right? is there a better way to do this?)
- Finally create a decade column for binning years.
- Since rating data only comes from people who were born in certain years, filter the data to focus on the years we have rating data birthdates from.

- For the rating data, filter to exclude irrelevant names, and create a decade column based on birth years.
- Then, recode a location column that corresponds to which region participants are most aligned with.

- Plot the data with two overlaid 2D density plots.

#### location cute plot

```{r}
#| warning: false

# intersect(top_pop, top_rate_eu)
set.seed(231); c("Andrea","Ashley","James","Alex","Morgan","Laura","William","Charlie","Robin") -> filter_name; annual.regional.breakdown |> 
  filter(name %in% filter_name,
         name != "Godzilla",
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North\nAmerica",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         #log10.afab = case_when(afab > 0 ~ log10(afab), .default = abs(rnorm(1,sd=0.001))),
         #log10.amab = case_when(amab > 0 ~ log10(amab), .default = abs(rnorm(1,sd=0.001))),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |>
  ungroup() |> 
  filter(decade >= 1950) |> #filter(name == "William", region == "Oceania") ##|> #summary()
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
#  geom_point(alpha = 1, shape = ".", color = "black") +
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(
                                   location.influence == "__other" ~ location.longest,
                                   .default = location.influence),
                                 region = case_when(
                                   location.influence %in% c("Canada",
                                                             "United States of America") ~
                                     "North\nAmerica",
                                   location.influence %in% c(
                                     "UK - England and Wales",
                                     "Ireland",
                                     "UK - Scotland") ~ "Europe",
                                   location.influence %in% c("Australia",
                                                             "New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1950),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity",
                        bins = 15) +
#   geom_point(data = rating_data |> 
#                    filter(name %in% filter_name,
#                           name != "Godzilla") |>
#                    mutate(decade = round(birthyear, digits = -1),
#                           location.influence = case_when(
#                             location.influence == "__other" ~ location.longest,
#                             .default = location.influence),
#                           region = case_when(
#                             location.influence %in% c("Canada",
#                                                       "United States of America") ~
#                               "North\nAmerica",
#                             location.influence %in% c("UK - England and Wales",
#                                                       "Ireland","UK - Scotland") ~ 
#                               "Europe",
#                             location.influence %in% c("Australia",
#                                                       "New Zealand") ~ "Oceania")) |> 
#               filter(decade >= 1950),
#             aes(x = fem/100,
#                 y = masc/100),
#             color = "black",
#             shape = 4,
#             size = 1,
#             alpha = .5) +

  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  #geom_density2d() +
  #
  geom_density2d_filled(aes(alpha = after_stat(level)),
                        contour_var = "ndensity", bins = 50) +

  geom_abline(slope = 1, intercept = 0, color = "white", linewidth = .5, alpha = .5) +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.6,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(region~name) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  xlab("afab/typicality") +
  ylab("amab/typicality") +
  ggtitle(paste0("Population influence on ratings for a set of sample names across regions"),
          subtitle = "Grayscale = population; Color = ratings; Age of influence = birthyear") +
  NULL
```

#### longitude plot??

```{r}
c("Andrea","Ashley","James","Alex","Morgan","Laura","William","Charlie","Robin") ->filter_name; annual.regional.breakdown |> 
  filter(name %in% filter_name) |> 
  mutate(decade = round(year, digits = -1)) |> 
  group_by(name, region, decade) |> 
  summarise(afab = sum(afab),
            amab = sum(amab),
            n = n(),
            .groups = "drop")
```

```{r}
#| warning: false

# intersect(top_pop, top_rate_eu)
set.seed(231); c("Andrea","Ashley","James","Alex","Morgan","Laura","William","Charlie","Robin") -> filter_name; annual.regional.breakdown |> 
  filter(name %in% filter_name,
         name != "Godzilla",
         region != c("Northern Ireland")) |> #group_by(region) |> summarise(n = n())
  mutate(region = case_when(region %in% c("Canada",
                                          "USA") ~ "North\nAmerica",
                            region %in% c("England and Wales",
                                          "Ireland",
                                          "Scotland") ~ "Europe",
                            region %in% c("Australia",
                                          "New Zealand") ~ "Oceania")) |> 
  group_by(name,region) |> 
  mutate(yr.max = case_when(max(afab)>max(amab)~max(afab), .default = max(amab)),
         #log10.afab = case_when(afab > 0 ~ log10(afab), .default = abs(rnorm(1,sd=0.001))),
         #log10.amab = case_when(amab > 0 ~ log10(amab), .default = abs(rnorm(1,sd=0.001))),
         log10.afab = log10(afab),
         log10.amab = log10(amab),
         logprop.afab = log10.afab/log10(yr.max),
         logprop.amab = log10.amab/log10(yr.max),
         decade = round(year, digits = -1)) |>
  ungroup() |> 
  filter(decade >= 1950) |> #filter(name == "William", region == "Oceania") ##|> #summary()
  ggplot(aes(x = logprop.afab,
             y = logprop.amab)) +
  theme_bw() +
  
#  geom_point(alpha = 1, shape = ".", color = "black") +
  
  geom_density2d_filled(data = rating_data |> 
                          filter(name %in% filter_name,
                                 name != "Godzilla") |>
                          mutate(decade = round(birthyear, digits = -1),
                                 location.influence = case_when(
                                   location.influence == "__other" ~ location.longest,
                                   .default = location.influence),
                                 region = case_when(
                                   location.influence %in% c("Canada",
                                                             "United States of America") ~
                                     "North\nAmerica",
                                   location.influence %in% c(
                                     "UK - England and Wales",
                                     "Ireland",
                                     "UK - Scotland") ~ "Europe",
                                   location.influence %in% c("Australia",
                                                             "New Zealand") ~ "Oceania")) |> 
                          filter(decade >= 1950),
                        aes(x = fem/100,
                            y = masc/100),
                        contour_var = "ndensity",
                        bins = 15) +
   geom_point(data = rating_data |> 
                    filter(name %in% filter_name,
                           name != "Godzilla") |>
                    mutate(decade = round(birthyear, digits = -1),
                           location.influence = case_when(
                             location.influence == "__other" ~ location.longest,
                             .default = location.influence),
                           region = case_when(
                             location.influence %in% c("Canada",
                                                       "United States of America") ~
                               "North\nAmerica",
                             location.influence %in% c("UK - England and Wales",
                                                       "Ireland","UK - Scotland") ~ 
                               "Europe",
                             location.influence %in% c("Australia",
                                                       "New Zealand") ~ "Oceania")) |> 
               filter(decade >= 1950),
             aes(x = fem/100,
                 y = masc/100),
             color = "black",
             shape = 4,
             size = 1,
             alpha = .5) +

  scale_fill_viridis_d(option = "turbo", end = .9, begin = .1) +
  
  ggnewscale::new_scale_fill() +
  
  #geom_density2d() +
  #
  geom_density2d_filled(aes(alpha = after_stat(level)),
                        contour_var = "ndensity", bins = 50) +

  geom_abline(slope = 1, intercept = 0, color = "white", linewidth = .5, alpha = .5) +
  
  scale_fill_grey(start = 0, end = .7) +
  scale_alpha_discrete(range = c(.6,0)) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0,1))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,1)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(decade~name) +
  coord_equal() +
  #gganimate::transition_time(decade) +
  
  xlab("afab/typicality") +
  ylab("amab/typicality") +
  ggtitle(paste0("Population influence on ratings for a set of sample names across regions"),
          subtitle = "Grayscale = population; Color = ratings; Age of influence = birthyear") +
  NULL
```

### ethnicity

```{r}
rating_data |> 
  mutate(ethnicity = str_to_lower(ethnicity),
         ethnicity.cat = case_when(ethnicity %in% c("white mixed latinamerican",
                                                    "mixed",
                                                    "pkeh/anglo-indian",
                                                    "hispanic white") ~ "other",#"more than one",
                                   ethnicity %in% c("white/jewish",
                                                    "ashkenazi jewish, white-passing",
                                                    "ashkenazi jewish",
                                                    "white and jewish",
                                                    "white, ashkenazi jewish",
                                                    "white, jewish",
                                                    "ashkenazi jewish, white",
                                                    "white, ashkenazi") ~ "jewish",
                                   ethnicity %in% c("asian american",
                                                    "i am black but grew up mostly around white people (but my family is black).") ~ "other",
                                   .default = "white"),
         decade = round(birthyear, digits = -1),
         location.influence = case_when(location.influence == "__other" ~ location.longest,
                                        .default = location.influence),
         region = case_when(location.influence %in% c("Canada","United States of America") ~
                              "North\nAmerica",
                            location.influence %in% c("UK - England and Wales",
                                                       "Ireland","UK - Scotland") ~ 
                              "Europe",
                            location.influence %in% c("Australia","New Zealand") ~ 
                              "Oceania")) |> 
  group_by(ethnicity.cat,gender.cat,region) |> 
  summarise(n = n()/51,
            .groups = "drop") |> 
  pivot_wider(names_from = gender.cat,
              values_from = n,
              values_fill = 0)
```



